Output Summary

### 2021-06-23 03-post-process/output-plots.Rmd
Add a figure to output plots diagnosing issues from new broodstock removal

## AR(1) Coefficients

```{r}
post_summ(post, "kappa", Rhat = TRUE, neff = TRUE, digits = 3)
```

>>>>

# Misc

## Brood stock Removals

This figure shows the frequency that `Sb[y,k,s,o]` (spawners passed above weir, following broodstock removals) would go negative if not for the constraint `Sb[y,k,s,o] <- max(Ra[y,k,s,o] - n_broodstock[y,k,s,o], 0)`.

```{r, fig.width = 8, fig.height = 5}
Sb_post = post_subset(post, "^Sb[", matrix = TRUE)
p0 = array_format(colMeans(Sb_post == 0))
dimnames(p0) = dimnames(jags_data$n_broodstock)
years = as.numeric(dimnames(p1)[[1]])

par(mfcol = c(3,4), oma = c(1.5,1.5,0,0), mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
plot(p0[observable,1,1,1] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,3\\,(NOR)$"), ylim = c(0,1))
plot(p0[observable,2,1,1] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,4\\,(NOR)$"), ylim = c(0,1))
plot(p0[observable,3,1,1] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,5\\,(NOR)$"), ylim = c(0,1))
plot(p0[observable,1,2,1] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,3\\,(NOR)$"), ylim = c(0,1))
plot(p0[observable,2,2,1] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,4\\,(NOR)$"), ylim = c(0,1))
plot(p0[observable,3,2,1] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,5\\,(NOR)$"), ylim = c(0,1))
plot(p0[observable,1,1,2] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,3\\,(HOR)$"), ylim = c(0,1))
plot(p0[observable,2,1,2] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,4\\,(HOR)$"), ylim = c(0,1))
plot(p0[observable,3,1,2] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,5\\,(HOR)$"), ylim = c(0,1))
plot(p0[observable,1,2,2] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,3\\,(HOR)$"), ylim = c(0,1))
plot(p0[observable,2,2,2] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,4\\,(HOR)$"), ylim = c(0,1))
plot(p0[observable,3,2,2] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,5\\,(HOR)$"), ylim = c(0,1))
```
